Theories of deliberated preference

### 2018-02-25 simple.tex
Def minimal dec sit

Actually we will use only the $\ileadstopst$ and $\ileadstosst$ ternary relations from now on (and their negations $\ileadstose$ and $\ileadstope$), together with the property (A1) that $\ileadstopst \subseteq \ileadstope$
\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.} 
and (A2) that $\ileadstosst \subseteq \ileadstopst$
\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
the pair $(\ar, \ar')$ being understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$, and similarly for $\ileadstopst$).

When “both” is not observable, the same definitions hold, with $f_t(\ar, \ar') ≠ b$. It follows that $\ileadstopst = \ileadstosst$. We say in this case that $\ileadstost$ does not distinguish sure from possible. Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.

>>>>

As defined, $\ileadstost$ has the following properties. (A1) $\ileadstopst \subseteq \ileadstope$
\footnote{Equivalently: $\ileadstosst \subseteq \ileadstose$, $(\ar, \ar') \ileadstose ¬\prop ∨ (\ar, \ar') \ileadstope \prop$, $\ileadstopst \prop ⇒ ¬ (\ileadstosst ¬\prop)$, $\ileadstosst ¬\prop ⇒ ¬ (\ileadstopst \prop)$.} 
and (A2) that $\ileadstosst \subseteq \ileadstopst$
\footnote{Equivalently: $\ileadstose \subseteq \ileadstope$.}, 
and the pair $(\ar, \ar')$ is to be understood as unordered (thus $(\ar, \ar') \ileadstosst \prop ⇔ (\ar', \ar) \ileadstosst \prop$).

Note that these properties follow from the way the querying protocol is presented above, but actually these are the only properties required, thus any querying protocol that satisfies those qualify. When “both” is not observable, the same definitions hold, with $f_t(\ar, \ar') ≠ b$. It follows that $\ileadstopst = \ileadstosst$. We say in this case that $\ileadstost$ does not distinguish sure from possible. Thus, elements $\phi \in \Phi$ may be considered as simply equal to $\prop$ or $¬\prop$, as $(\prop, \text{sure})$ is treated exactly as $(\prop, \text{possible})$.
